---
title: "Pilot: NDVI Time Series of Living England AOI"
author: "SM"
date: "2023-06-16"
output: html_document
---

```{r setup, echo=FALSE, message=FALSE,warning=FALSE, error=FALSE}
library(sf)
library(sp)
library(terra)
library(raster)
library(dplyr)
library(caret)
library(caretEnsemble)
library(ForestTools)
library(lidR)
library(randomForest)
library(e1071)
library(rgdal)
library(rgeos)
library(Rcpp)
library(rmarkdown)
library(knitr)
library(MASS)
library(car)
library(reticulate)
library(rstudioapi)
library(leaflet)
library(magrittr)
library(jsonlite)
library(processx)
library(leafem)
library(crayon)
library(R6)
library(cli)
library(rgee)
#rgee::ee_install(py_env = "rgee") ## installtion necessary only once
#devtools::install_github(("gearslaboratory/gdalUtils"))
library(gdalUtils)
#library(gdalUtilities)
#webshot::install_phantomjs(force = TRUE)
#knit_hooks$set(webgl = hook_webgl)
#knit_hooks$set(rgl.static = hook_rgl)
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, error=FALSE, message = FALSE)
set.seed(123)
```

## Action:

The following report documents pilot code for evaluating spectral indices (NDVI) for identifying change in Living England AOI. This includes deployment of google earth engine through python and rgee package for data acquisition and rendering of spectral mosaics, as well as development of acccuracy metrics using caret modelling package in R.

### Assign Python(3.10.6) version in use
```{r, eval=FALSE}
reticulate::use_python("/usr/bin/python3.10",
                       required = TRUE)
reticulate::py_config()
```
### Initialize Earth Engine (& Google Cloud/Tidyverse API if needed)
```{r}
# Necessary only once in each environment/IDE
ee_Initialize() 
#ee_Initialize(user = 'seamusrobertmurphy@gmail.com', drive = TRUE, gcs = TRUE) 
```
### Derive DTM from Global LiDAR Data (SRTM) 
